Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-17 Grassmannian_cells.tex
Fixed Theorem 4.16

  \noindent{\bf Claim.}
  For any proper subset $J\subsetneq\{1,\ldots,n\}$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces with the following property:
  \begin{itemize}
    \item[($\dagger$)] For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and $J\subset I_0$ consider the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients}.
      For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
  \end{itemize}
  \vs

@@

  Choose any subset $I\subsetneq\{1,\ldots,n\}$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi_{m+1,I,j}$ and $\Phi_{m,I,j}$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
  There are two cases to consider.

  First suppose $I\subset I_0$.
  Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a decomposition into affine spaces which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
  \[\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)=\coprod_{k=1}^r C_k.\]

@@

  When $\tbfg=\udim\tilde P_{m+1}^I$, Proposition~\ref{fibers} shows that the fibers of $\Psi_{m+1,I,j}$ over $B_\ell\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ are empty exactly when 
  \begin{itemize}
    \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$ for all $U\in B_\ell$.
  \end{itemize}
  Otherwise, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
  For $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(V)\in C_k$.
  But then $\pi_{m+1}^{J,\bfI}(V)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(W)\ne0$ for all $W\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(V')\ne0$ for all $V'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.

  It remains to consider the case $j\notin I_0$.

\begin{comment}
\noindent {\bf Claim.} Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\geq 1$ be an arbitrary admissible sequence and $\underline{j_1}=(\uj,j_{1,l+1},\ldots,j_{1,n-1})\in I_{n-1}$. The quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ has a cell decomposition into affine spaces which is compatible with $\pi_{m,\uj}^{\bf j}$  in the following way: 
 Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ such that $\pi_m^{\bf j}(U)\neq 0.$
Then we have $\pi_{m,\uj}^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
\vs

>>>>

  \noindent{\bf Claim.}
  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a decomposition into affine spaces which are compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
  \begin{itemize}
    \item[($\dagger$)] For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
  \end{itemize}
  \vs

@@

  Choose any subset $I\subset I_0$ with $J\subset I$ and $|I\setminus J|=1$, say $I\setminus J=\{j\}$.
  This gives the short exact sequence \eqref{eq:truncated ses} inducing the maps $\Psi_{m+1,I,j}$ and $\Phi_{m,I,j}$ between quiver Grassmannians from \eqref{eq:truncated CC} and \eqref{eq:truncated CC2}.
  Then by induction on $|I|$, each quiver Grassmannian $\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ has a decomposition into affine spaces which is compatible with $\pi_{m+1}^{I,\bfI}$, say 
  \[\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)=\coprod_{k=1}^r C_k.\]

@@

  When $\tbfg=\udim\tilde P_{m+1}^I$, Proposition~\ref{fibers} shows that the fibers of $\Psi_{m+1,I,j}$ over $B_\ell\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I)$ are empty exactly when 
  \begin{itemize}
    \item $m=2$ with $\tbff_{(2,\alpha_j^{-1})}\ne0$ or $\tbff_{(1,e)}\ne0$;
    \item $m\ge3$, with $\pi_{m,j}^\bfJ(U)=0$ for all $U\in B_\ell$.
  \end{itemize}
  When the fibers of $\Psi_{m+1,I,j}$ are not empty, for $1\le k\le r$ we obtain an affine cell in $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ of the form $B_\ell\times C_k\times\AA^d$ with~$d=\langle\tbfg,\udim\tilde P_{m,j}-\tbff\rangle$.
  For $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ which is contained in such a cell, we have $\pi_{m+1}^{J,I}(V)\in C_k$.
  But then $\pi_{m+1}^{J,\bfI}(V)\ne0$ if and only if $\pi_{m+1}^{I,\bfI}(W)\ne0$ for all $W\in C_k$ and thus $\pi_{m+1}^{J,\bfI}(V')\ne0$ for all $V'$ in this cell $B_\ell\times C_k\times\AA^d$ of $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$.
\begin{comment}
\noindent {\bf Claim.} Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\geq 1$ be an arbitrary admissible sequence and $\underline{j_1}=(\uj,j_{1,l+1},\ldots,j_{1,n-1})\in I_{n-1}$. The quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ has a cell decomposition into affine spaces which is compatible with $\pi_{m,\uj}^{\bf j}$  in the following way: 
 Let $U\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m}^{\uj})$ such that $\pi_m^{\bf j}(U)\neq 0.$
Then we have $\pi_{m,\uj}^{\bf j}(U')\neq 0$ for all $U'\in C_U$ where $C_U$ is the cell which contains $U$.
\vs
